\title{Big Data in Safe Driver Prediction}

\author{Jiaan Wang}
\affiliation{%
  \institution{Indiana University Bloomington}
  \streetaddress{3209 E 10 St}
  \city{Bloomington} 
  \state{IN} 
  \postcode{47408}
}
\email{jervwang@indiana.edu}

\author{Dhawal Chaturvedi}
\affiliation{%
  \institution{Indiana University Bloomington}
  \streetaddress{2679 E 7th St}
  \city{Bloomington} 
  \state{Indiana} 
  \postcode{47408}
}
\email{dhchat@iu.edu}

\begin{abstract}

    For years, people have been trying to reduce their automobile
    insurance bills. Insurance companies claim that price will be
    reduced for good drivers and raised for bad ones. However,
    inaccuracies in their data predictions lead to the exact
    opposite. The dataset being used is released by Porto Seguro,
    an auto and homeowner insurance company from Brazil. It
    consists of information from several hundred thousands of
    policyholders. The goal is to predict the probability an auto
    insurance policyholder files a claim the next year using
    classification algorithms. A good prediction with decent
    accuracy can correctly adjust prices for policyholders.
    
\end{abstract}

\keywords{i523, HID233, Big data, Classification, Safe Driving, Predictive Analytics, Neural Networks}

\maketitle

\section{Introduction}

``Big data is defined as structured and unstructured large volume of data. The amount of data is not that important but how businesses and industries use the big data. Big data is analyzed for patterns and systems that are used for strategies and decisions. Let’s take for example the big data that smart cars collect when driving. As the vehicle travels, it collates driving patterns based on the routes. It then sends this set of information to the car’s computer. The data collated is then forwarded to some servers. These data are analyzed and used to improve the safety features of the smart car'' \cite{Walker2017safety}.

``Big data is fundamental in making decisions for product development. When the big data is analyzed, it helps determine root causes of defects or failures. This allows industries to improve on their products. For example, as a BMW driver uses the driver assistance plus safety features, it also collects data based on driving habits. If more drivers are prone to speeding when approaching intersections, manufacturers use these data to improve on the safety feature. It may add a sensor that detects intersections based on GPS data. On the other hand, driving routes are also useful data. Take for example the technology of Google Street view. It shows views of streets, routes, and locations. The big data from the driving routes can be used by Google to update the maps and make sure that roads are updated'' \cite{Walker2017safety}.

``Predictive analytics can be a powerful decision-making tool within various parts of fleet operations. It’s used in many major industries such as retail, finance and insurance to forecast what is most likely going to happen in the future — it’s a popular risk assessment tool. To illustrate the potential uses in the world of fleet, safety and safety-related decisions provide a great example of how predictive analytics can impact fleet operations'' \cite{Suizo2015decisions}.

``Fatal vehicle collisions are one of the leading causes of death in the U.S., according to the Centers for Disease Control. While this may not come as much of a surprise considering these types of fatalities frequently make headlines, what should be more alarming is the fact that many of these collisions are preventable'' \cite{Suizo2015decisions}.

``With the nature of fleet business often revolving around its employees being on the road, fleets are significantly impacted by these statistics. Automotive Fleet reports most company drivers average 20,000 miles per year, with more fleets experiencing an increase in preventable accidents. The primary cause of this uptick in preventable fleet accidents points to driver distraction that now contributes to the 25-30 percent of all fleet-related accidents, reports Automotive Fleet'' \cite{Suizo2015decisions}.

``With over 40,000 deaths each year coming from traffic-related collisions and accidents, it's a clear sign that improving road safety is a top priority across the nation. Advances in technology are helping reduce accidents and improving overall driver safety through a variety of methods. Here are the top 4 ways that technology will help improve road safety in the coming years'' \cite{Mills2017safety}.

``For years, insurance companies have used estimates of your annual mileage to determine your car insurance rates. But with recent changes in technology, insurers now have an unprecedented ability to judge your actual driving habits. Armed with detailed data on how often you slam on the brakes and what times of day you're on the road, insurance companies are increasingly relying on precise, technological means of assessing risk — and using that information to set your monthly premiums'' \cite{Fung2016turn}.

``Along with computer controlled vehicles, data collection is vital to ensuring that we understand where and why accidents happen. The black box technology that has been famously used to track airplanes and help identify the cause of crashes is now being used in other vehicles. Black box technology is fairly simple, inexpensive, and easy to deploy on a wide scale of cars. The benefits of the technology are we will be able to track the exact time, speeds, position, and other factors related to car collisions and accidents. As this data is studied, we will be able to better understand trends and reasons behind car crashes and use this data to prevent future incidents. South Korea was the first country to deploy black box technology in their taxi services and immediately noticed a 14 percent decrease in traffic accidents the following year. The death toll and injury rate associated with traffic accidents also decreased by as much as 20 percent'' \cite{Mills2017safety}.

``Through telematics and other data, predictive models make it possible for fleets to make more educated decisions with less expense — it provides support for decisions, making them more efficient and effective, or in some cases, can be used to automate an entire decision-making process. Considered the most revolutionary technological step of the “Big Data” era, predictive analytics has quickly become one of the most advanced forms of customized risk management'' \cite{Suizo2015decisions}.

``Predictive analytics is ideal for risky driving analysis, for example. The challenge with identifying high-risk drivers is the most transparent records such as driving records, traffic violations, and accident reports, and may not always indicate a driver with the highest potential risk. Armed with information on driving behaviors through telematics data, companies can put drivers in safety training programs tailored to their risky driving behaviors before a collision occurs. Information about a driver’s behavior can also be used to determine how likely an individual is to be involved in an accident as well as the costs associated with that risk'' \cite{Suizo2015decisions}.

``Outside of safety, by leveraging and analyzing data to provide insights into vehicle and equipment usage, driver behavior, and fleet productivity schedules, fleet managers can discover various areas where cost efficiency can be applied. This includes preventive maintenance, which can greatly contribute to cost cutting and increased productivity. Trending out maintenance data creates the opportunity to predict component failure, and provide real-time transaction repair costs, helping fleets to shape best-in-class maintenance policies and procedures'' \cite{Suizo2015decisions}.

``Looking at information such as past usage, maintenance and overall total cost of ownership, fleets can also use predictive analytics for vehicle procurement strategies. Predictive analytics can help in other ancillary ways as well. One fleet that implemented the driver safety score model in its operations noted an increase in personal communication, with drivers sharing information and essentially comparing notes and scores. After using the program for several months, the client reported drivers calling in to discuss safety proactively and in a positive way, whereas in the past, safety had only been a source of punishment for a driver when they made a mistake, so it was often a topic that drivers avoided. This truly changed how safety was viewed by the driver population and the organization as a whole'' \cite{Suizo2015decisions}.

``Predictive models come in various forms, depending on the behavior or event they are predicting. Most generate a score, similar to a credit score, with a higher score indicating a higher likelihood of the given behavior or event occurring. Predictive analytics encompasses a variety of techniques from statistics, modeling, machine learning and data mining that analyze current and historical facts to make predictions about future or otherwise unknown events'' \cite{Suizo2015decisions}.

``Predictive analytics tells the customers, with as much accuracy as possible, what will happen in a few weeks or other chosen time frame — not what has happened in the past, but what the most likely outcome for a specific driver or vehicle is in the future and why that’s the case. Predictive analytics gives fleets an opportunity to think proactively rather than reactively'' \cite{Suizo2015decisions}.

``Using safety as an example, by analyzing a driver’s particular driving style via telematics data, a safety report can be compiled highlighting the risks inherent to the driver and help coach safer driving habits. Drivers are classified into categories of risk based off the probability that a driver will be in a collision. By making these probabilities easy to assess, a safety score can help fleets make better decisions on how to prioritize risk within their operations. The primary objectives of a safety score would be to identify risky drivers prior to a collision to provide the driver an opportunity to modify those behaviors and prevent the collision from occurring'' \cite{Suizo2015decisions}.

``Like other types of risk assessment programs, predictive analytics is not intended to be a magic bullet. It is only the beginning and requires a total commitment from the organization, fleet personnel, and driver to turn the model’s efficacy into reality. It requires strong management commitment in order to succeed. The most successful users are organizations that involve all departments in the process at an early stage including operations, safety, HR and IT. One reason previous predictive analytics projects have failed is due to the failure to achieve alignment and full enterprise adoption'' \cite{Suizo2015decisions}.

``The main component in leveraging fleet analytics is assembling and analyzing actual fleet data. In order to develop accurate and valuable predictive models, it’s important to understand the challenges you want to address first to ensure that the models are solving a real-world problem. Real data and real problems are the key'' \cite{Suizo2015decisions}.

``Start by choosing the area of greatest need (e.g., safety, maintenance, or workers compensation). Large volumes of data can result in hours of analysis with no real return in the way of fleet operational and cost optimization. One step to curb data overload is to simply ensure the data accumulated is the data actually needed. Data and analytical models should align with overall fleet goals and provide measurable and meaningful results. One good place to start leveraging analytical data is to understand your organization’s goals beyond fleet as well. Being able to meet these goals through the use of measurable analytics is the objective'' \cite{Suizo2015decisions}.

``Next, identify the key elements and the type of data that will make up your fleet’s predictive model. The necessary data is then extracted, which should be validated by the fleet. Analytics involves more than just having the data — fleets must ensure they understand what the data is telling them and why it will help them predict a future event'' \cite{Suizo2015decisions}.

``The best way to balance the accuracy and timeliness of the predictive model, such as the driver safety score described earlier, is to run the models every few weeks or the time frame that makes the most sense for your operations. Giving it at least a few weeks provides safety and operational groups enough time to take action, while still accurately reflecting the changes that indicate risk. This is balanced with trying to minimize operational burden since most have limited time, whether it’s coaching drivers or needing to get a vehicle in for repair before a major breakdown'' \cite{Suizo2015decisions}.

``To further the safety example, the program’s success could be measured by the percentage of drivers involved in collisions that were predicted accurately in the 90-day period prior to the collision. More specifically, it would examine the data of the risky driver to determine if that individual was classified at the highest risk level at least one-third of the time in the 90 days prior. This example uses an odds ratio, which is the measure of association between an exposure and an outcome. To explain further, it looks at the odds a driver will get into a collision in the next 90 days given a particular score'' \cite{Suizo2015decisions}.

``Although predictive analytics is most commonly used with fleets who were early adopters of telematics, it is something that more and more fleets are seeing the value in. With predictive analytics, fleets can proactively take action and make educated decisions that positively impact their organizations by reducing risk, whether tied to improving safety and costs or decreasing the work behind the decision-making process'' \cite{Suizo2015decisions}.

\section{Big data in auto insurance}

``Traditional car insurance prices all start at the same place: risk pools. Customers are categorized by demographics such as age and sex and then the company makes guesses based on statistics about their predicted risk of future accidents. That means the rates you get are only as good as whatever information the company chooses to include in your “profile”. And that data usually has very little to do with how you actually drive. The price you pay is mostly based on the historical risk of other people who have similar profiles. Some of the risk factors make sense - like if you have previously filed several claims, you’re probably more likely to have one again in the future. Others, however, such as education or whether or not you drive an imported car, have less to do with your driving habits but still count toward your price. And the most useful measure of risk - your actual driving behavior - that’s hardly used by anyone'' \cite{Rippe2017unfair}.

``Major car insurance carriers have access to vast quantities of information and computational power, used for the purpose of determining risk, coverage, and premiums. It’s a complex affair, involving figuring out how to condense a dozen or more different factors into a single price. But you might not realize just how much Big Data goes essentially unused - representing a missed opportunity for traditional carriers. These providers use a number of different methods to compute rates for the various forms of coverage sold to drivers, but not all of these systems perform as optimally as they could. A recent study of the uses of data mining in auto insurance found that there are more accurate possible methods of identifying high-risk drivers and separating them from low-risk drivers, including one recent model incorporating 16 risk factors to provide extremely high accuracy in risk appraisal'' \cite{Rippe2017unfair}.

``The shortcomings of traditional car insurance aren’t inevitable. Today, there are easier ways for good drivers to get the premiums they deserve. Root is the first fully mobile car insurance company designed to fit your on-the-go lifestyle, insuring only good drivers in order to ensure the best rates. Our mobile-first approach fits your on-the-go lifestyle - no clunky proprietary devices are needed, only the app. Drive with Root onboard for two to three weeks, and we’ll deliver you a personalized quote based on your unique driving data. You can easily select the coverage you want to buy and pay immediately via your phone. It’s that simple'' \cite{Rippe2017unfair}.

``Usage-Based Insurance (UBI), a somewhat recent innovation by auto insurers, closely aligns driving behaviors with premium rates for auto insurance. Mileage and driving behavior can be captured by applications on your smartphones as well as OBD devices or embedded in-car technology provided directly by the auto manufacturer. With the first UBI programs, insurance companies provided insurance discounts to reward good driving behavior. Now those discounts are combined with other rewards and benefits like roadside assistance and vehicle theft recovery. By capturing big data around driving behavior, insurance companies will be able to quickly determine fault when accidents do occur. Insurance companies will be able to do this by understanding precise movements of each car, combining behavioral data, such as hard braking and accelerating, with real-time contextual data, including road conditions and the weather, and even video from on-board cameras'' \cite{Shafer2016industry}.

``Increasingly, Big Data – make that Big Brother? – is in the front seat of your car, and is affecting how much you pay for auto insurance. In theory, “usage-based” or “pay-as-you-drive” insurance sounds perfectly reasonable and fair. Instead of profiling drivers based just on the traditional factors—age, location of residence, history of accidents and traffic violations, and so on—a small device is installed into the car that monitors how drivers actually drive. These programs, including Allstate’s “Drivewise” and Progressive’s “Snapshot,” have been available for several years in select locations on a strictly voluntary basis. Drivers have been welcoming these devices into their cars because, at least for now, they’re being presented on a “discount only” basis. That is, drivers whose habits are deemed to be sufficiently safe—easy on the brakes and gas pedal, limited long-haul trips or driving during “risky” hours—can see their premiums drop by 5 percent, 10 percent, sometimes upwards of 30 percent. On the downside, consumer advocates worry that these devices cause drivers to give up their privacy, and that no one really knows what the long-term repercussions could be by welcoming insurance companies inside cars. Just about every article written on the topic includes the phrase Big Brother. Now, reports the Wall Street Journal, these programs are expanding in a big way. State Farm, the country’s largest auto insurer, has plans to promote its “Drive Safe and Save” program in nearly every state by the end of 2013. The main selling point is that by accepting these devices in their vehicles, customers can prove that they’re safe drivers who deserve cheaper insurance rates'' \cite{Tuttle2013habits}.

``One of the first usage-based insurance (UBI) programs to hit the market was Progressive’s partnership with General Motors roughly a decade ago. The program implemented a mileage-based discount to users by using GPS technology. Many UBI programs still use this technology, but there have been many advancements. Insurers can now know how, where, and when policyholders drive. UBI variations include “pay as you drive” (PAYD), “pay how you drive” (PHYD), and other distance- and telematics-based insurance options. The term “telematics” refers to the merging of telecommunications and information science for accurate data assessment. The benefits of telematics-based UBI programs include the ability to increase accident response time and track lost or stolen vehicles. Additionally, a popular method of analyzing UBI is through plug-in devices. These devices, which connect via the OBD-II port of a car, don’t necessarily track location, but they do report more accurate and detailed information about vehicle usage. While telematics and GPS are the most common ways to track driving behaviors, future innovations will likely include using a car or phone’s GPS and accelerometer to monitor abrupt alterations in speed and other unsafe behavior. In December 2015, Liberty Mutual tested volunteer drivers with this technology in order to expand their RightTrack program, and State Farm is testing their own voluntary phone tracking platform. According to SMA Research, it is expected that nearly 70 percent of all auto insurance carriers will use telematics-based UBI by 2020. UBI methods are on the rise and will continue to grow in accuracy and accessibility'' \cite{Firm2016insurance}.

``On a different scale, the connected car is changing the way companies view automotive insurance. Vehicles today send thousands of data points to servers every second, detailing everything from their location to braking and their speed. In the future, vehicle-to-infrastructure solutions will communicate high-resolution road conditions—down to the pothole and puddle level—on a real-time basis. Insurance companies can use this data to make real-time decisions that manage risk, perhaps even using telematics and automated-driving technology to advise drivers on the least dangerous route to take. The use of big data in insurance is already transforming the industry. For example, Ford has partnered with IVOX, developer of the DriverScore app. This uses privacy-enhanced technology to tell insurance companies how drivers are performing in order to potentially lower their premiums. Similarly, connected homes are getting better at communicating their environmental conditions'' \cite{Bradbury2017game}. 

``One of the most important uses is for setting policy premiums. In insurance, efficiency is an important keyword. Insurers must set the price of premiums at a level which ensures them a profit by covering their risk, but also fits with the budget of the customer – otherwise they will go elsewhere. A great example of this formula in action is motor insurance. While drivers (particularly younger ones) often complain about the high prices, this is a market where there is a huge amount of competition and shopping around on price comparison services is common among customers. As a result an insurance business is made or broken on its ability to accurately assess the risk posed by a particular driver and offer them a competitive, but profit-making premium'' \cite{Marr2015forever}.

``Many insurers now offer telemetry-based packages, where actual driving information is fed back to their system to a personalized, highly accurate profile of an individual customer’s behavior can be built up. Using predictive modelling as mentioned above, the insurer can work out an accurate assessment of that driver’s likelihood to be involved in an accident, or have their car stolen, by comparing their behavioural data with that of thousands of other drivers in their database. This data is sometimes captured and transmitted from a specially installed box fitted to the car or, increasingly, from an app on a driver’s smart-phone. US insurers Progressive offer a great example of a business which has committed to working with data to enhance its services. It has created what is calls its Business Innovation Garage where technologists known as “mechanics” produce and road-test innovations. One project involves rendering 3D images of damaged vehicles using computer graphics. Images are scanned in from cameras to create 3D models allowing structured data to be recorded on the condition and damage to a vehicle'' \cite{Marr2015forever}.

\section{Current Applications}

``Predictive analytics are being employed in interesting new ways to improve safety. Telematics solutions have long monitored events like hard braking and speeding to flag unsafe driver behaviors.  But today, this driver event data is being enriched with other data streams to actually predict the likelihood of a specific driver having an accident. A company called SmartDrive Systems goes even further in their efforts to predict accidents.  They are enriching the telematics data with video feeds from road facing and interior facing cameras.  The company is combining asset sensor with driver sensor data to do better driver safety analytics and ultimately make better predictions'' \cite{Banker2016accident}.

``SmartDrive Systems is a predictive analytics supplier whose solution is based on a private cloud architecture.  In other words, all of their customers’ data is captured by the company; they have telematics and video on four billion miles driven, of which they scored almost 200 million events.   SmartDrive’s customer agreements allow them to analyze all the customer data so they can continue to improve their algorithms.  “We are constantly tuning and improving our algorithms,” Mr. Mitgang said. The combination of telematics and video has allowed their scientists to better interpret the telematics data. By reading the telematics data, and seeing what happened, they were able to determine, for example, that turning more than 165 degrees within a certain turning radius and time window was a risky U-turn on a roadway. SmartDrive also detected additional patterns to avoid false trigger activation in large open areas such as parking lots and truck stops'' \cite{Banker2016accident}.

``Indiana State Police decided to take a different approach, and are making their predictive crash analytics program available to the public, as well as troopers. A color-coded Daily Crash Prediction map, which went online in November, pulls together data that includes crash reports from every police agency in the state dating to 2004, daily traffic volume, historical weather information and the dates of major holidays, said First Sgt. Rob Simpson. The online map pinpoints where a crash is likely, ranging from a very low to a high probability. It also highlights prior crash sites and displays information about the date and cause, whether EMS was called, if there was a fatality, and if drugs or alcohol were involved. As of late January, the site had nearly 4,800 page visits'' \cite{Bergal2017sites}.

``Liberty Mutual, the country's third-largest property-and-casualty insurer, took the latest step in that direction Monday when it announced a partnership with Subaru. Beginning later this year, Subaru drivers who have paid for the automaker's Starlink infotainment system will be able to download an app to their cars that notifies them when they are accelerating too aggressively or braking too hard. The app is part of Liberty Mutual's RightTrack program, which gives drivers a 5 percent discount on their rates for enrolling and additional discounts up to 30 percent for heeding the app's guidance on driving safely'' \cite{Fung2016turn}. 

\section{Neural Networks Analysis}


\section{Results and Discussion}



\section{Conclusion}


\begin{acks}

  The authors would like to thank Dr. Gregor von Laszewski for his
  support and suggestions to write this paper.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 
